\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
	
	%\bibitem{citation-1-name-here}Cite all academic papers, libraries, datasets, and tools used. \url{<url here>}
	
	\bibitem{BFS-ref-one}
	Cormen, Thomas H.; Leiserson, Charles E.; Rivest, Ronald L. \emph{Introduction to Algorithms.  (4ed.)} "Section 20.2: Breadth-first search", MIT Press. pp. 554-262.
	ISBN 978-0-262-04630-5. 
	
	\bibitem{Bellman-ford-ref-one}
	Cormen, Thomas H.; Leiserson, Charles E.; Rivest, Ronald L. \emph{Introduction to Algorithms.  (4ed.)} "Section 22.1: The Bellman–Ford algorithm", MIT Press. pp. 612–616.
	ISBN 978-0-262-04630-5.
	
	\bibitem{Dijikstra-ref-one}
	Cormen, Thomas H.; Leiserson, Charles E.; Rivest, Ronald L. \emph{Introduction to Algorithms.  (4ed.)} "Section 22.3: Dijikstra's algorithm", MIT Press. pp. 620-625.
	ISBN 978-0-262-04630-5.  
	
	\bibitem{A-star-Search-ref-one}
	Russell, Stuart J.; Norvig, Peter (2018). 
	\emph{Artificial intelligence: A Modern approach (3th ed.)}. "Section 3.5.2: A* Search", Pearson. pp. 93-99. ISBN 978-0-134-61099-3.
	
	\bibitem{Bidirectional-ref-one}
	Robert C. Holte, Ariel Felner, Guni Sharon, Nathan R. Sturtevant (2016)
	\emph{Bidirectional Search That Is Guaranteed to Meet in the Middle}
	\url{https://www.cs.du.edu/~sturtevant/papers/MMaaai.pdf}
	
	\bibitem{Contraction-hiearchies-ref-one}
	Robert Geisberger, Peter Sanders, Christian Vetter (2012)
	\emph{Exact Routing in Large Road Networks Using Contraction Hierarchies}
	\url{https://publikationen.bibliothek.kit.edu/1000028701/142973925}
	
	\bibitem{ALT-ref-one}
	Fabian Fuchs (2010)
	\emph{On Preprocessing the ALT algorithm}.
	\url{https://www.fabianfuchs.com/fabianfuchs_ALT.pdf}
	
	\bibitem{HL-ref-one}
	Ittai Abraham, Daniel Delling, Andrew V. Goldberg (2010)
	\emph{A Hub-Based Labeling Algorithm for Shortest Paths on Road Networks}.
	\url{https://www.microsoft.com/en-us/research/wp-content/uploads/2010/12/HL-TR.pdf}
	
	
\end{thebibliography}
